MaxEnt: What is it good for?

### 2015-06-29 ms.tex
Two new references

The principle is very intuitively compelling
and there are some axiomatic arguments in its favour
\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.

@@

>>>>

The principle is very intuitively compelling
and there are some axiomatic arguments in its favour
\citep[e.g.][]{shore_johnson, 2006AIPC..872...31C, 2010arXiv1008.4831K}
and counterexamples to alternatives \citep[e.g.][]{presse}.
However, MaxEnt has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.

@@

\bibitem[Pressé et al(2013)]{presse}
Pressé, S., et al. ``Nonadditive entropies yield probability distributions with biases not warranted by the data.'' Physical review letters 111.18 (2013): 180604.

\bibitem[Shore and Johnson(1980)]{shore_johnson}
Shore, J.E., and Johnson, R.. ``Axiomatic derivation of the principle of maximum entropy and the principle of minimum cross-entropy.'' Information Theory, IEEE Transactions on 26.1 (1980): 26-37.
